%-------------------------
% Resume in Latex
% Author : Audric Serador
% Inspired by: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{newtxtext,newtxmath} % Times New Roman font

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\fontsize{16}{20}\selectfont\fontfamily{ptm}\selectfont\mdseries
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Custom commands
\begin{document}
\include{custom-commands}

%-------------------------------------------%
%%%%%%  RESUME STARTS HERE  %%%%%

% Define custom marine blue color
\definecolor{MarineBlue}{RGB}{15,40,130}
\definecolor{StrongerBlue}{RGB}{0,102,204} % New stronger blue color

%----------HEADING----------%
\begin{center}
  {\color{MarineBlue}\fontfamily{ppl}\fontsize{36}{40}\selectfont\scshape\mdseries Aryamann Tomar} \\ \vspace{5pt}
  \seticon{faPhone} \ \small +91-8955252787 \,
  $|$ \, \href{mailto:tejalpoonia2001@gmail.com}{\color{StrongerBlue}\seticon{faEnvelope} \underline{tejalpoonia2001@gmail.com}} \,
  $|$ \, \href{https://www.linkedin.com/in/tejal-poonia-03357b218/}{\color{StrongerBlue}\seticon{faLinkedin} \underline{linkedin.com/TejalPoonia}} \,
  $|$ \, \href{https://github.com/Tejal-poonia}{\color{StrongerBlue}\seticon{faGithub} \underline{github.com/Tejal-poonia}}
\end{center}

%-----------EDUCATION-----------%
\section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology (NIT), Hamirpur}{2019 -- 2023}
      {Bachelor of Technology in Mechanical Engineering}{\textbf{CGPI: 8.54/10}}
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------%
\section{Work Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Goods and Services Tax Network}{July 2023 -- Present}
    {Software Engineer}{Delhi}
    \resumeItemListStart
        \resumeItem{Developed a fusion filter in C++ for optimizing and consolidating data sets, improving data efficiency by 40\%.}
        \resumeItem{Architected and developed a logging server using C++ and OOP principles, utilizing RADS and shared memory for communication between the server and various client applications.}
        \resumeItem{Designed a flexible JSON message format using rapidJSON for dynamic messages from different applications. Developed parsers and routing logic to interpret and relay messages based on content and metadata.}
    \resumeItemListEnd
 
    \resumeSubheading
    {Maruti Suzuki Pvt. Ltd.}{June 2022 -- July 2022}
    {Automobile Industrial Trainee}{Jaipur}
    \resumeItemListStart
        \resumeItem{Performed comprehensive analysis of wheels and tires on various vehicles}
        \resumeItem{Conducted essential tire services including changes, rotations, and wheel alignments}
        \resumeItem{Executed precise tire and wheel assembly balancing to optimize vehicle performance}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Dynamic Routing and Mapping} $|$ \emph{C++, Data Structure and Algorithms}}{}
    \resumeItemListStart
        \resumeItem{Implemented Dijkstra’s and A* algorithms to dynamically calculate the fastest routes, improving navigation efficiency by 30.}
        \resumeItem{Integrated GNSS for real-time vehicle tracking with 80\% accuracy, ensuring precise and reliable location data.}
        \resumeItem{Developed a system for real-time guidance by dynamically computing distances to upcoming turns, enhancing travel optimization.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Path Find Visualizer} $|$ \emph{C++, Data Structure and Algorithms, OOPS}}    {}
    \resumeItemListStart
        \resumeItem{Developed a web application for pathfinding in 2D mazes using Dijkstra's, BFS, and DFS algorithms.}
        \resumeItem{Implemented user-interactive features including customizable start/end points and grid generation.}
        \resumeItem{Designed advanced functionality such as weighted nodes, obstacle placement, and pathfinding animations.}
    \resumeItemListEnd
    
    % \resumeProjectHeading
    % {\textbf{NetflixGpt \href{https://netflixgpt-60854.web.app/}{\ \faLink}} $|$ \emph{React, Redux, Firebase}}{}
    % \resumeItemListStart
    %     \resumeItem{Designed and implemented a robust movie search functionality using OpenAI APIs, resulting in a user experience similar to Netflix.}
    %     \resumeItem{Utilized OpenAI APIs to enable ChatGPT-powered search queries, successfully retrieving over 5,000 movies from the TMDB Movie Database.}
    %     \resumeItem{Integrated Google Firebase for SignIn/SignUp, securing and managing authentication for over 1,000 users.}
    % \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------%
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: C, C++, Python, HTML, CSS} \\
		\textbf{Technologies}{: Django, SQL, AWS} \\
		\textbf{Concepts}{: OOPS, DSA, System Design, DBMS, API}
	}}
    \end{itemize}

%-----------ACHIEVEMENTS & EXTRACURRICULAR-----------%
\section{Achievements \& Extracurricular Activities}
\resumeItemListStartTight
    \resumeItem{Achieved 8th Kyu (Yellow Belt) in Seiko Kai Karate International India.}
    \resumeItem{Holder of B and C Certificates in National Cadet Corps (NCC).}
    \resumeItem{Received Certificate of Appreciation for dedicated membership in Ek Bharat Shreshtha Bharat Club, NITH (2020-2021).}
    \resumeItem{Awarded Gargi Pursakar (Gargi Award) for excellent performance in High School (2016).}
    \resumeItem{NCC (National Cadet Corps) - April 2019 to 2022: Served as Cadet in Army NITH, participated in training camps and activities.}
    \resumeItem{Active participant in Martial Arts Karate Academy events at NITH (2019-Present).}
\resumeItemListEnd

%-------------------------------------------%
\end{document}